\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-18 icse/main.tex
Written 4.4 Rule Assistant

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

\begin{abstract}
While JavaScript is initially invented for client-side in web browsers,
JavaScript engines are now embedded in many other types of host software.
Despite its popularity, JavaScript semantics are complicated because of its
dynamic nature. Thus, the formal analysis and verification of JavaScript programs
require its formal semantics. Several researches proposed formal semantics
of JavaScript based on ECMAScript, the official specifications of JavaScript.
However, the existing approaches are fully manual and only target ECMAScript 5.1.
It is a critical problem to understand recent JavaScript programs
because ECMAScript is annually updated from 2015. Thus, already five more updates
after ECMAScript 5.1.

To alleviate such problems, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
specifications. \( \tool \) generates JavaScript parser for the given grammar written
in \( \bnfes \), an extended BNF used in ECMAScript specifications.
Our tool also converts each abstract algorithm written in structured natural
languages into functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications. The compilation from algorithms to \( \ires \) functions
is defined with \textit{compile rules}. We apply \( \tool \) into the next proposed
version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
in test262, the official ECMAScript conformance test suite.
Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
by adding only \inred{XX} minor compile rules.
\end{abstract}

>>>>

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage[noend]{algorithm,algpseudocode}
\usepackage{enumitem}

@@

\begin{abstract}
JavaScript was initially designed for client-side code in web browsers,
but its engine is now embedded in various kinds of host software.
Despite its popularity, since the JavaScript semantics is complex
especially due to its dynamic nature, understanding and reasoning
about JavaScript programs are challenging tasks.  Thus,
researchers have proposed several attempts to define the formal semantics
of JavaScript based on ECMAScript, the official JavaScript specification.
However, the existing approaches are manual, labor-intensive, and
error-prone, and they all target only the ECMAScript 5.1 version.
This problem is critical in understanding recent JavaScript programs
because ECMAScript has been annually released since 2015, which made
already five updates after ECMAScript 5.1.

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript specifications.  It also converts each
abstract algorithm written in a structured natural language into
functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications.  The compilation from algorithms to
\( \ires \) functions is defined with \textit{compile rules}.
We applied \( \tool \) to the next proposed version, ECMAScript 2020,
and the automatically extracted semantics passed all \inred{XXXXX} tests 
in test262, the official ECMAScript conformance test suite.
\inred{Moreover, \( \tool \) also successfully extracts
semantics for \inred{XX} proposed features by adding only \inred{XX}
minor compile rules.}
\end{abstract}
